% begin Abstract
\clearpage
\chapter*{Abstract}

\paragraph{ } The Private Bus Passenger Transportation System is the most widely used Public Transportation System in Sri Lanka. It is used as the primary transport method for passengers within Colombo, the most populous city in the country, as well as between Colombo and other cities as well as suburbs.

However, the system is rife with inefficiencies and shortcomings. Delays, overcrowded buses and bus strikes are commonplace and the service is of poor quality. The problems in the system do not merely affect the transportation industry but has a knock-on effect to all walks of daily life for the people in the country. The productivity of the workforce suffers due to this inefficiency in the main public transport system.

The biggest problem that the commuters outline is the need to improve the service in terms of its schedule reliability and passenger overcrowding. Meanwhile, the bus operators complain that the revenue leakage is a major issue and needs to be rectified. However, the status quo continues without any solutions and these problems continue to haunt the average commuter.

Research into the issues as well as comments from frequent commuters has shown that the underlying cause is the lack of a proper Information System to assist the stakeholders in their decision making processes. Therefore, this research analyses the problems prevalent in the system and provides a solution to help minimize/eliminate the existing problems. The project identifies key aspects in the solution prototype and generalizes the results so that the concept can be applied to other developing countries with similar environments.