% begin literature published

\chapter*{Literature published from research}

\paragraph{} A research paper on the work related to this research project was submitted to the 2013 European, Mediterranean \& Middlle-Eastern Conference on Information Systems (EMCIS). The paper was accepted subject to changes. The paper was an analysis of transportation systems in developing countries and how an Information Systems solution would help solve the problems faced in the public transportation domain. The details of the paper are listed below.

\section*{Title}

"A Transportation Management Information System for Public Transport in Developing Countries."

\section*{Authors} 

\begin{itemize}
\item Aftha Jaldin
\item Dr. Shiromi Arunatilake
\end{itemize}

\section*{Abstract}

\paragraph{} Public Transportation Management in developing countries presents a more challenging environment than its counterpart in developed nations. And, as in any Public Transport System, the Scheduling Process provides the framework in which the Transport Service operates. It is responsible for the formulation of timetables, vehicle and crew scheduling, and crew rostering. Although this is the most important part of the transport system, it is the most difficult to manage. The varied inputs to the process, the lack of proper infrastructure and improper technology and processes available all lead to a unique problem in terms of Public Transportation Management in a developing country. Therefore it is imperative for a system to cater to these limitations and meet the demands of a developing country specifically. Therefore, this paper proposes an alternative system to aid the Schedulers in their capacity to formulate timetables and schedule vehicles and crew. The system will also act as an information portal to commuters to obtain information about transport modes and associated routes as well as other related information. The paper uses the case of the Western Province Bus Transportation System in Sri Lanka as an example to draw conclusions regarding the proposed information system.


